External Validation

### 2021-02-02 FEM_R/validation.Rmd
WIP - mostly done but trying to figure out the best way to show all the plots together

# Rename cols to enable reshaping
male_au <- male_au %>%
                dplyr::rename(m_6064 = X60.64, m_6569 = X65.69, m_7074 = X70.74, 
                       m_7579 = X75.79, m_8084 = X80.84, m_8589 = X85.89, 
                       m_9094 = X90.94, m_9599 = X95.99, m_100 = Over.100) %>%
                select(!Total)

female_au <- female_au %>%
                dplyr::rename(f_6064 = X60.64, f_6569 = X65.69, f_7074 = X70.74, 
                       f_7579 = X75.79, f_8084 = X80.84, f_8589 = X85.89, 
                       f_9094 = X90.94, f_9599 = X95.99, f_100 = Over.100) %>%
                select(!Total)

# Now need to reshape these datasets to long format
pivoted.male <- pivot_longer(data = male_au,
                             cols = m_6064:m_100,
                             names_to = c('Gender', 'Age_Group'),
                             names_sep = '_')

pivoted.female <- pivot_longer(data = female_au,
                             cols = f_6064:f_100,
                             names_to = c('Gender', 'Age_Group'),
                             names_sep = '_')

@@

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Hearte Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)

@@

# Now row bind the datasets
combined <- rbind(newFEM, ageUK)
# Sort
combined <- arrange(combined, source, Condition, Gender, Age_Group)

@@

@@

>>>>

# Rename cols to enable reshaping
male_au <- male_au %>%
                dplyr::rename(m_6064 = X60.64, m_6569 = X65.69, m_7074 = X70.74, 
                       m_7579 = X75.79, m_8084 = X80.84, m_8589 = X85.89, 
                       m_9094 = X90.94, m_9599 = X95.99, m_100p = Over.100) %>%
                select(!Total)

female_au <- female_au %>%
                dplyr::rename(f_6064 = X60.64, f_6569 = X65.69, f_7074 = X70.74, 
                       f_7579 = X75.79, f_8084 = X80.84, f_8589 = X85.89, 
                       f_9094 = X90.94, f_9599 = X95.99, f_100p = Over.100) %>%
                select(!Total)

# Now need to reshape these datasets to long format
pivoted.male <- pivot_longer(data = male_au,
                             cols = m_6064:m_100p,
                             names_to = c('Gender', 'Age_Group'),
                             names_sep = '_')

pivoted.female <- pivot_longer(data = female_au,
                             cols = f_6064:f_100p,
                             names_to = c('Gender', 'Age_Group'),
                             names_sep = '_')

@@

# REMOVE CONDITIONS FROM ageUK THAT ARE NOT IN FEM (may change in future)
#ageUK <- filter(ageUK, Condition != c('Asthma', 'Depression', 'Severe Mental Health Condition'))
ageUK <- filter(ageUK, Condition != 'Asthma', Condition != 'Depression', Condition != 'Severe Mental Health Conditions')

@@

# Rename all the conditions to fit ageUK
# NOTE: Lung disease is not a perfect match, as ageUK only contains info on COPD
#       Therefore only validation from this will be that FEM is higher than ageUK
newFEM$Condition <- gsub("hearte", "Heart Problems", newFEM$Condition)
newFEM$Condition <- gsub("hibpe", "Hypertension", newFEM$Condition)
newFEM$Condition <- gsub("stroke", "Stroke", newFEM$Condition)
newFEM$Condition <- gsub("diabe", "Diabetes", newFEM$Condition)
newFEM$Condition <- gsub("lunge", "Lung Disease (COPD)", newFEM$Condition)
newFEM$Condition <- gsub("cancre", "Cancer", newFEM$Condition)
newFEM$Condition <- gsub("demene", "Dementia", newFEM$Condition)

@@

# Now row bind the datasets
combined <- rbind(newFEM, ageUK)
# Specify factor levels for age group
combined$Age_Group <- factor(combined$Age_Group, levels = c('6064', '6569', '7074', '7579', '8084', '8589', '9094', '9599', '100p'))
# Sort
combined <- arrange(combined, source, Condition, Gender, Age_Group)

@@

# First try to plot the whole dataset in a facet grid
# This isn't perfect, and it's pretty complicated to plot altogether
ggplot(data = combined, aes(x = Age_Group, y = value, width = 0.7)) +
  geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
  facet_wrap(~Condition)

@@

# Now instead, lets plot an individual condition - Hypertension

# First extract all hypertension info
hyper <- filter(combined, Condition == 'Hypertension')

# Big dirty plot
ggplot(data = hyper, aes(x = Age_Group, y = value, width = 0.7)) +
  geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
  labs(title = 'Hypertension', x = 'Age Group', y = 'Proportion')

# Next, lets try an all female and all male example
